R Notebook

### 2017-02-14 manuscript/draft.Rmd
Create box on good forecasting practices

>>>>

## Box 1: Ten simple rules for making and evaluating ecological forecasts

### 1. Compare multiple modeling approaches

Typically ecological forecasts use one modeling approach or a small number of
related approaches. By fitting and evaluating multiple modeling approaches we
can learn more rapidly about the best approaches for making predictions for a
given ecological quantity. This includes comparing process based and data-driven
models.

### 2. Use time-series data when possible

Forecasts describe how systems are expected to change through time. While some
areas of ecological forecasting focus primarily on time-series data, others
primarily focus on using spatial models and space-for time substitutions. Using
ecological and environmental time-series data allows the consideration of actual
dynamics from both a process [@treddenick2016a] and error structure perspective.

### 3. Pay attention to uncertainty

Understanding confidence in a forecast is just as important as understanding the
average or expected outcome. Failing to account for uncertainty can result in
overconfidence in highly uncertain outcomes leading to poor decision making and
erosion of confidence in ecological forecasts. Models should explicitly include
sources of uncertainty where possible and evaluations of forecasts should assess
the accuracy of uncertainties as well as point estimates [@dietz2017].

### 4. Use predictors related to the question

Many ecological forecasts use data that is readily available and easy to work
with. While ease of use is a reasonable consideration it is also important to
include predictor variables that are expected to relate to the ecological
quantity being forecast and dynamic time-series of predictors instead of
long-term averages. Investing time in identifying and acquiring better predictor
variables may have at least as many benefits as using more sophisticated
modeling techniques.

### 5. Assess how forecast accuracy changes with time-lag

In general the accuracy of forecasts decreases with the length of time into the
future being forecast [@petch2015]. This decay in accuracy and associated
forecast horizons should be considered when evaluating forecasts and comparing
models.

### 6. Include an observation model

Ecological observations are influenced by both the underlying processes and how
the system is sampled. When possible forecasts should model the factors
influencing the observation of the data.

### 7. Validate using hindcasting

To evaluate the expected accuracy and uncertainty of forecasts assess the
performance of these forecasts within existing time-series data.

### 8. Publicly archive forecasts

To allow the future evaluation of the accuracy and uncertainty of forecasts the
forecast values and/or models should be archived so that they can be assessed
after new data is generated [@mcgill2012]. Enough information should be provided
to allow an unambiguous assessment of the forecast performance.

### 9. Make short-term and long-term predictions

In cases where long-term predictions are the primary goal, short-term should
also be made to accommodate the time-scales of planning and management decisions
and to allow the accuracy of the forecasts to be quickly evaluated
[@treddenick2016a];

### 10. Compare forecasts to simple baselines

Compare the accuracy of the forecasts to simple baselines such as the
time-series average to determine if the modeled forecasts are more accurate than
the naive assumption that the world is static.
